\documentclass[a4paper]{article}
\usepackage[a4paper,top=2cm,bottom=2.5cm,left=1.5cm,right=1.5cm,marginparwidth=1.75cm]{geometry}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{listings}
\usepackage{helvet}

%% Sets page size and margins
\usepackage{float}

%% Useful packages
\usepackage{amsmath}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{ {./images/} }
% \DeclareGraphicsExtensions{.pdf,.jpg,.png}

%% defined colors
\definecolor{Blue}{rgb}{0,0,0.5}
\definecolor{Green}{rgb}{0,0.75,0.0}
\definecolor{LightGray}{rgb}{0.6,0.6,0.6}
\definecolor{DarkGray}{rgb}{0.3,0.3,0.3}

%% Packages added by me
\usepackage{url}
\usepackage{hyperref}
\usepackage{quoting}
\usepackage[font={small,it}]{caption}
\usepackage{subcaption}

\graphicspath{{./images/}}

\title{Assignment: Applied Data Science Capstone project}
\author{Marc Jellema} \date{\today}

\begin{document}
\maketitle

\abstract{
This report is a deliverable for my capstone project \textit{Battle of the neighbourhoods}, part of my graduation for my \textbf{IBM Data Science Professional certificate}. The assignment was to define a challenge that was to be solved by using the FourSquare API. Nowadays almost anything you need can be found online, including public data sets to use freely. I tapped into the public domain data sets with key figures from the Netherlands. Combining the FourSquare with the Dutch key figures showed a strong correlation between house prices and the number of restaurants in the neighbourhood. Before this correlation is to be used in other algorithms, I strongly advice to use more detailed data sets to underwrite the conclusion found during my assignment. Feel free to send me an email on {\href{mailto:mjellema@omnia.nl}{mjellema@omnia.nl}} if you like to discuss this report in more detail.

% TODO abstract needs to hold the executive summary as well

\section*{Introduction}
I tasked myself with the assignment to find additional ways to enhance automatic estimation of house prices in the Netherlands. The use of the \textbf{FourSquare} API is mandatory for this assignment, part of the IBM Data Science professional certificate \cite{IBM1}. As a tech savvy person myself, I'd heard of FourSquare and I do remember seeing the FourSquare logo on venues in the past, but never came across its footprint in the Netherlands. Wondering if I could use the FourSquare API in finding an answer for a challenge in the Netherlands, I did some research and as it turned out, the FourSquare database was more than comprehensive enough to use for data science challenges in the Netherlands as well. Not knowing a single person actively using FourSquare to let their friends know where they check-in, it puzzled me how FourSquare actually accumulates their data. James D. Walsh wrote a nice article \cite{FS1} on how FourSquare accomplishes this. Enough about FourSquare for now, let's focus on introducing the question I want to answer with help of the FourSquare API and the data it can provide:
\medskip
\begin{quote}
\textit{Based on \textbf{FourSquare} data, can we find a correlation between the average house price, the number of restaurants and the number of inhabitants in the provinces of the Netherlands?}
\end{quote}
\medskip
Although the COVID pandemie is having an impact on the overall economy world wide, it seems house prices have not yet taken a hit due to the pandemic. Startups like \textbf{Promodomo} \cite{Promo} use algorithms to calculate house prices, even when they are not on the market yet. Algorithms like Promodomo's always benefit from additional sources to enrich their calculation. Searching for a correlation based on FourSquare data is just one of the many possibilities to augment the estimation of house prices and this is why I choose to take this challenge and come up with answers in this capstone project of my IBM Data Science Professional certificate. 
\input{Chapters/Data}
\input{Chapters/Methodology}
\input{Chapters/Results}
\input{Chapters/Discussion}
\input{Chapters/Conclusion}
\input{Chapters/Acknowledgments}

\bibliographystyle{ieeetr}
\bibliography{bibfile}

\end{document}